### 2017-12-13 Paper/main.tex
Updates from ShareLaTeX

In order to be sure of the forecasting prediction we computed the confusion matrix of each model and we get the following information:
\begin{itemize}
    \item the model out perform the naive algorithm;
    \item the model failed to predict in a consistent way whether the price was going up or down;
    \item either the models alone failed to do so;
    \item the plain ARIMA performed purely in comparison with the hybrid model.
\end{itemize}

>>>>

In order to be sure of the forecasting prediction we computed the confusion matrix for each model represented at \ref{confusionmatrix}. A information:
\begin{itemize}
    \item the ARodel out perform the naive algorithm;
    \item the model failed to predict in a consistent way whether the price was going up or down;
    \item either the models alone failed to do so;
    \item the plain ARIMA performed purely in comparison with the hybrid model.
\end{itemize}

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth, ]{Paper/images/Confusion_matrix.png}
    \caption{Plot of the aggregate P/L per stock}
    \label{confusionmatrix}
\end{figure}
